### 2015-02-27 icfp15-servo/open.tex
Clarify open JS problems.

\paragraph{Just-in-time code.} JavaScript engines dynamically produce native code that is
intended to execute more efficiently than an interpreted strategy.
Unfortunately, this area is a large source of security bugs.
These bugs come from two sources.
First, there are potential correctness issues.
Many of these optimizations are only valid when certain conditions of the calling
code and environment hold, and ensuring the specialized code is called only when those
conditions hold is non-trivial to verify.
Second, dynamically producing and compiling native code and patching it into memory
while respecting all of the invariants required by the JavaScript runtime (e.g., the
garbage collector's tracing hooks or free vs. in-use registers) is also a challenge.

\paragraph{JavaScript object rooting.} Objects from the JavaScript
heap  are held onto by \Cplusplus{} objects --- and sometimes vice-versa.
Today, all modern engines manually manage the boundary code to handle tracing
these objects, and this leads to leaking objects or, worse, freeing objects that
are still in use.
The lack of a typical garbage collector for these objects also means that cycles
between \Cplusplus{} and JavaScript need to be broken through ad-hoc means.

>>>>

\paragraph{Just-in-time code.} JavaScript engines dynamically produce native code that is
intended to execute more efficiently than an interpreted strategy.
Unfortunately, this area is a large source of security bugs.
These bugs come from two sources.
First, there are potential correctness issues.
Many of these optimizations are only valid when certain conditions of the calling
code and environment hold, and ensuring the specialized code is called only when those
conditions hold is non-trivial.
Second, dynamically producing and compiling native code and patching it into memory
while respecting all of the invariants required by the JavaScript runtime (e.g., the
garbage collector's read/write barriers or free vs. in-use registers) is also a challenge.

\paragraph{JavaScript object rooting.} Objects from the JavaScript
heap are held onto by \Cplusplus{} objects, and often vice-versa as well.
Today, all modern engines manually manage the boundary code to handle tracing
these foreign pointers. Any errors in this code lead to leaked object or, worse,
freeing objects that are still in use.
The lack of a holistic garbage collector also means that cycles
between \Cplusplus{} and JavaScript must be broken on an ad-hoc basis, or
a specialized cycle collector must be integrated that understands cross-language
references.
